%%%%%%%%%%%%%%%%%%%%%%%%%%  Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{99}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%Modeles de matrices

\bibitem{ABK} M.Aganagic, V.Bouchard and A.Klemm,
``Topological strings and (almost) modular forms'',
hep-th/0607100.

\bibitem{ADKMV} M.Aganagic, R.Dijkgraaf, A.Klemm, M.Mari\~{n}o and C.Vafa,
``Topological strings and integrable hierarchies'',
{\em Commun. Math. Phys.} {\bf 261} (2006) 451, \\
hep-th/0312085.

\bibitem{Ak96} G.Akemann,
``Higher genus correlators for the Hermitian matrix model with multiple cuts'',
{\em Nucl. Phys.} {\bf B482} (1996) 403, hep-th/9606004

\bibitem{AkAm} G.Akemann and J.Ambj{\o}rn,
``New universal spectral correlators'',
{\em J.Phys.} {\bf A29} (1996) L555--L560, cond-mat/9606129.

\bibitem{Mth1} A.Alexandrov, A.Mironov and A.Morozov,
`` M-Theory of Matrix Models'', hep-th/0605171.

\bibitem{Mth2} A.Alexandrov, A.Mironov and A.Morozov,
``Instantons and Merons in Matrix Models'',
hep-th/0608228.

\bibitem{ACKM}
J.Ambj{\o}rn, L.Chekhov, C.F.Kristjansen and Yu.Makeenko,
``Matrix model calculations beyond the spherical limit'',
{\em Nucl.Phys.} {\bf B404} (1993) 127--172; Erratum ibid. {\bf B449} (1995) 681,
hep-th/9302014.

\bibitem{ambjornrmt} J. Ambj{\o}rn, B. Durhuus, J. Fr{\"o}hlich, "Diseases of triangulated random surface models, and possible cures", Nuclear Physics B, Volume 257, p. 433-449.

\bibitem{BBT} O. Babelon, D. Bernard, M. Talon, {\em Introduction to Classical Integrable Systems }
(Cambridge University Press).

\bibitem{BergSchif} S. Bergman, M. Schiffer, ``Kernel functions and elliptic differential equations in mathematical physics'', Academic Press Inc., Publishers, New York, NY, 1953.

\bibitem{BCOV} M.Bershadsky, S.Cecotti, H.Ooguri and C.Vafa,
``Kodaira-Spencer theory of gravity and exact results for quantum string amplitudes'',
{\em Commun. Math. Phys.} {\bf 165} (1994) 311.

\bibitem{Marco2} M. Bertola, ''Two-matrix model with semiclassical potentials and extended Whitham hierarchy'',
{\em  J.Phys.} {\bf A39} 8823-8856  (2006),  hep-th/0511295.

%\bibitem{Marcopath} M. Bertola, "Biorthogonal polynomials for 2-matrix models with semiclassical potentials", nlin.SI/0605008.

\bibitem{MarcoF} M. Bertola, ''Free Energy of the Two-Matrix
Model/dToda Tau-Function'',
preprint CRM-2921 (2003), hep-th/0306184.

%\bibitem{BDE}  G. Bonnet, F. David, B. Eynard, ``Breakdown of universality in multi-cut matrix models'',
%{\em  J.Phys.} {\bf A33} 6739-6768  (2000).

\bibitem{BIPZ} E. Brezin, C. Itzykson, G. Parisi, and J.B. Zuber,
{\em Comm. Math. Phys.} {\bf 59}, 35  (1978).

\bibitem{Chekh} L.Chekhov,
``Genus one corrections to multi-cut matrix model solutions'',
{\em Theor. Math. Phys. } {\bf 141} (2004) 1640--1653, hep-th/0401089.

\bibitem{chekhovhe} L. Chekhov,
``Matrix models with hard walls: Geometry and solutions'',
{\em J.Phys.} {\bf A39} (2006) 8857-8894, hep-th/0602013.

\bibitem{ec1loopF} L.Chekhov, B.Eynard,
``Hermitian matrix model free energy: Feynman graph technique for all genera'',
{\em J. High Energy Phys.} {\bf JHEP03} (2006) 014, hep-th/0504116.

\bibitem{ChEynbeta} L.Chekhov, B.Eynard,
``Matrix eigenvalue model: Feynman graph technique for all genera'',
{\em J. High Energy Phys.} {\bf JHEP 0612} (2006) 026, math-ph/0604014.

\bibitem{CEO} L.Chekhov, B.Eynard and N.Orantin,
``Free energy topological expansion for the 2-matrix model'',
{\em J. High Energy Phys.} {\bf JHEP12} (2006) 053, math-ph/0603003.

\bibitem{DKK} J.M.Daul, V.Kazakov, I.Kostov,
``Rational Theories of 2D Gravity from the Two-Matrix Model'',
{\em Nucl.Phys.} {\bf B409} (1993) 311-338, hep-th/9303093.

\bibitem{DReview} R.Dijkgraaf,
``Intersection theory, integrable hierarchies and topological field theory'',
in J.Frohlich and al. (eds), {\em New symmetry principles in quantum field theory},
 Plenum Press, p.95; hep-th/9201003.

\bibitem{DV}
R.Dijkgraaf and C.Vafa,
``Matrix Models, Topological Strings, and Supersymmetric Gauge Theories'',
{\em Nucl.Phys.} {\bf 644} (2002) 3--20, hep-th/0206255;
``On Geometry and Matrix Models'',
{\em Nucl.Phys.} {\bf 644} (2002) 21--39, hep-th/0207106;
``A Perturbative Window into Non-Perturbative Physics'',
hep-th/0208048.

\bibitem{DW} R.Dijkgraaf and E.Witten,
``Mean field theory, topological field theory, and multimatrix models'',
{\em Nucl.Phys.} {\bf B342} (1990) 486--522.

\bibitem{Virasoro} F. David,
``Loop equations and nonperturbative effects in two-dimen\-sional quantum gravity''.
{\em Mod.Phys.Lett.} {\bf A5} (1990) 1019.

\bibitem{davidRMT} F. David, "Planar diagrams, two-dimensional lattice gravity and surface models",
Nuclear Physics B, Volume 257, p. 45-58.

\bibitem{ZJDFG} P. Di Francesco, P. Ginsparg, J. Zinn-Justin,
``2D Gravity and Random Matrices'',
{\em Phys. Rep.} {\bf 254}, 1 (1995).

\bibitem{PDFgraph} P. Di Francesco, "2D gravity, matrix models and graph combinatorics",
Lecture given in Les Houches, {\em applications of random matrices in physics}, june 2004,
math-ph/0406013.

\bibitem{BookPDF} P. Di Francesco, P. Mathieu, D. S\'en\'echal, "Conformal field theory", Springer, 1999.

\bibitem{Dubrovin1} B. Dubrovin, ``Geometry of 2D topological field theories'',
{\em Integrable Systems and Quantum Groups}, Montecalini, Terme, 1993.
Editor: M.Francaviglia, S. Greco and
{\em Springer Lecture Notes in Math.}  {\bf 1620} (1996), 120Đ348.

\bibitem{Dubrovin2} B.Dubrovin, Y.Zhang, ``Bihamiltonian Hierarchies in 2D Topological Field
Theory At One-Loop Approximation'',
{\em Commun.Math.Phys.} {\bf 198} (1998) 311-361, hep-th/9712232.

\bibitem{Dysondet} F.J. Dyson, "correlations between the eigenvales of a random matrix", Comm. Math. Phys. {\bf 19} (1970) 235-50.

%\bibitem{EML} 

\bibitem{eynmetha} B. Eynard, M.L. Mehta, "Matrices coupled in a chain: eigenvalue correlations", J. Phys. A: Math. Gen. {\bf 31} (1998) 4449-4456.

\bibitem{eynloop1mat} B. Eynard, ``Topological expansion for the 1-hermitian matrix model correlation functions'',
JHEP/024A/0904, hep-th/0407261.

\bibitem{eynm2m} B. Eynard, ``Large N expansion of the 2-matrix model'',
{\em JHEP} {\bf 01} (2003) 051, hep-th/0210047.

\bibitem{eynm2mg1} B. Eynard, ``Large N expansion of the 2-matrix model,
multicut case'',
preprint SPHT03/106, ccsd-00000521, math-ph/0307052.

\bibitem{eynhardedges} B.Eynard,
``Loop equations for the semiclassical 2-matrix model with hard edges'',
{\em J.Stat.Mech.} {\bf 0510} (2005) P006, math-ph/0504002.

\bibitem{EKK}
B.~Eynard, A.~Kokotov, and D.~Korotkin,
``$1/N^2$ corrections to free energy in Hermitian two-matrix model'',
hep-th/0401166.

\bibitem{eynmultimat} B. Eynard, ``Master loop equations, free energy and correlations for the chain of matrices'',
{\em J. High Energy Phys.}  {\bf JHEP11}(2003)018, xxx, hep-th/0309036, ccsd-00000572.

\bibitem{courseynard} B. Eynard ``An introduction to random
matrices'', lectures given at Saclay, October 2000, notes available at
http://www-spht.cea.fr/articles/t01/014/.

%\bibitem{eylooprat} B.Eynard,
% ``Loop equations for the semiclassical 2-matrix model with hard edges'',
%math-ph/0504002.

\bibitem{eyno} B.Eynard, N.Orantin,
``Topological expansion of the 2-matrix model correlation functions: diagrammatic rules for a residue formula'',
{\em J. High Energy Phys.} {\bf JHEP12}(2005)034, math-ph/0504058.

\bibitem{eynform} B.Eynard,
`` Formal matrix integrals and combinatorics of maps'', \\
math-ph/0611087.

\bibitem{EMO} B.Eynard, M.Mari\~{n}o, N.Orantin,
``Holomorphic anomaly and matrix models'', hep-th/0702110.

\bibitem{EOSym} B.Eynard, N.Orantin,
``Mixed traces and free energy symetry'',
in preparation.

\bibitem{ECK1} B. Eynard, C. Kristjansen, ``Exact solution of the O(n) model on a random lattice'', Nuc. Phys. B455 577-618, (1995), hep-th/9506193.

\bibitem{ECK2} B. Eynard, C. Kristjansen, ``More on the exact solution of the O(n) model on a random lattice, and an investigation of the case |n|>2'',
 Nuc. Phys. B466 463-487, (1996), hep-th/9512052.

\bibitem{Farkas} H.M. Farkas, I. Kra, ''Riemann surfaces'' 2nd edition, Springer Verlag, 1992.

\bibitem{Fay} J.D. Fay, ''Theta functions on Riemann surfaces'', Springer Verlag, 1973.

\bibitem{Fay2} J.D. Fay, ``Fourrier coefficients of the resolvent for a Fuchsian group'', J. Reine Angew. Math. {\bf 293/294} (1977) 143-203.

\bibitem{IZK} C.Itzykson, J.B.Zuber,
``Combinatorics of the Modular Group II: The Kontsevich integrals'',
{\em Int.J.Mod.Phys.} {\bf A7} (1992) 5661-5705, hep-th/9201001 .

\bibitem{klemm} M. x. Huang, A.Klemm, S.Quackenbush,
``Topological String Theory on Compact Calabi-Yau: Modularity and Boundary Conditions'',
hep-th/0612125.

\bibitem{KazakovRMTcrit} VA Kazakov, IK Kostov, AA Migdal,
"Critical properties of randomly triangulated planar random surfaces", Physics Letters B, 1985.

\bibitem{KazakovRMT} V.A. Kazakov, "Bilocal regularization of models of random surfaces"
Physics Letters B, Volume 150, Issue 4, p. 282-284.

\bibitem{Kazakovloop} V.A. Kazakov,
"The appearance of matter fields from quantum fluctuations of 2D-garvity", Modern Physics Letters A, Vol. 4, No. 22 (1989) 2125-2139.

\bibitem{Kazakov} V.A. Kazakov, ``Ising model on a dynamical
planar random lattice: exact solution'',
{\em Phys Lett.} {\bf A119}, 140-144 (1986).

\bibitem{KazMar} V.A. Kazakov, A. Marshakov, ''Complex Curve of the
Two Matrix Model and its Tau-function'',
{\em J.Phys.} {\bf A36} (2003) 3107-3136, hep-th/0211236.

\bibitem{KharMar} S.Kharchev, A.Marshakov, ``On $p-q$ duality and explicit solutions in $c<1$ 2d gravity models'',
hep-th/9303100.

\bibitem{KPZ} V.G. Knizhnik, A.M. Polyakov, A.B. Zamolodchikov, Mod. Phys. Lett {\bf A3} (1988) 819.

\bibitem{kontsevitch} M.Kontsevitch,
``Intersection theory on the moduli space of curves and the matrix Airy function'',
{\em Funk. Anal. Prilozh.} {\bf 25} (1991) 50-57;
Max-Planck Institut preprint MPI/91-47, MPI/91-77.

\bibitem{Kos} I.K.Kostov,
`` Conformal field theory techniques in random matrix models'',
hep-th/9907060.

\bibitem{kostovhirota} I.K. Kostov, "Bilinear functional equations in 2d quantum gravity", \\
hep-th/9602117.

\bibitem{KoKo} A.Kokotov, D.Korotkin,
`` Bergmann tau-function on Hurwitz spaces and its applications'',
math-ph/0310008.

\bibitem{KoKo2} A.Kokotov, D.Korotkin,
`` Tau functions on Hurwitz spaces'',
{\em Math. Phys., Analysis and Geom.} {\bf 7} (2004), no. 1, 47-96 ,math-ph/0202034.

\bibitem{Kri} I.Krichever
``The $\tau$-function of the universal Whitham
hierarchy, matrix models and topological field theories'',
{\em Commun.Pure Appl.Math.} {\bf47} (1992) 437; hep-th/9205110

\bibitem{krichwitham} I.M. Krichever, ``The $\tau$-function of the universal Whitham hierarchy, matrix models and topological field theories'', hep-th/9205110.


\bibitem{MMtopo}  M. Mari\~no, "Les Houches lectures on matrix models and topological strings",
Lecture given in Les Houches, {\em applications of random matrices in physics}, june 2004, hep-th/0410165.

\bibitem{MMM} A.Marshakov, A.Mironov, A.Morozov,
``On Equivalence of Topological and Quantum 2d Gravity'',
{\em Phys. Lett.} {\bf B274} (1992) 280, hep-th/9201011.

\bibitem{Mehta} M.L. Mehta, {\em Random Matrices},2nd edition,
(Academic Press, New York, 1991).

\bibitem{Rauch} H.E. Rauch, `` Weierstrass points, branch points, and moduli of Riemann surfaces'',
{\em Comm. Pure Appl. Math.}, {\bf 12} (1959) 543-560.

\bibitem{staudacher} M. Staudacher,
`` Combinatorial solution of the 2-matrix model'',
{\em Phys. Lett.} {\bf B305} (1993) 332-338.

\bibitem{schaeffer} G. Schaeffer, ``Bijective census and random generation of Eulerian planar maps'',
{\em Electronic Journal of Combinatorics} {\bf 4} (1997) R20; see also ``Conjugaison d'arbres
et cartes combinatoires al\`{e}atoires'', PhD Thesis, Universit\`e Bordeaux I (1998).

\bibitem{thooft} G. 't Hooft, {\em Nuc. Phys.} {\bf B72}, 461 (1974).

\bibitem{TWlaw} C. Traicy, H. Widom, "Level-spacing distributions and the Airy kernel",
Comm. Math. Phys. {\bf 159} (1994) 151-174.

\bibitem{tutte} W.T. Tutte, ``A census of planar triangulations'',
{\em Can. J. Math.} {\bf 14} (1962) 21-38.

\bibitem{tutte2} W.T. Tutte, ``A census of planar maps'', 
{\em Can. J. Math.} {\bf 15} (1963) 249-271.

\bibitem{ellipticalf} Z.X. Wang, D.R. Guo, "Special Functions", World Scientific, 1989.

\bibitem{Zamozamo} A.B. Zamolodchikov, Al.B.Zamolodchikov,
"Structure Constants and Conformal Bootstrap in Liouville Field Theory",
Journal-ref: Nucl.Phys. B477 (1996) 577-605, hep-th/9506136.

\bibitem{Zamo} Al. Zamolodchikov,
"On the Three-point Function in Minimal Liouville Gravity",
hep-th/0505063.


\bibitem{PZinnmatext} P. Zinn-Justin, "Universality of correlation functions of hermitian random matrices in an external field", Commun. Math. Phys. 194, 631-650 (1998), cond-mat/9705044.


















\end{thebibliography}
